\speculake: Hiding Malware in Speculative Execution

### 2018-08-08 paper/conclusion.tex
update conclusion
conclusion pass

%In this paper 
We have presented \speculake, a model for hiding computation in
speculative execution that is fundamentally different than existing methods of
code obfuscation. Through a series of experiments we have classified the
capabilities and limitations of this speculative primitive and demonstrated
various example applications. We have demonstrated the potential
of using speculative execution in several applications, including a Turing
machine, SPASM emulator, remotely-triggered payloads, and AES decryption.
Currently analysis techniques for reverse engineering are insufficient to reason
about the behavior of these programs.

Given the benefits that speculative execution provides to an attacker and the
ease of such an attack, the feasibility of an \speculake exploit is high and is
not limited to data side-channels or process isolation violations, as was
originally thought in the wake of Spectre. The speculative primitive developed
in this work not only provides a guarded form of computation, but also enables
cryptographic protection against current analysis and debugging techniques.

>>>>

%In this paper 
We have presented \speculake, a model for hiding computation in speculative
execution that is fundamentally different than existing methods of code
obfuscation. Through a series of experiments we have classified the capabilities
and limitations of this speculative primitive and demonstrated various example
applications. We have demonstrated the potential of using speculative execution
in several applications, including a Turing machine, SPASM emulator,
remotely-triggered payloads, and AES decryption. We have also examined Intel's
responses to Spectre and Meltdown and noted how their defenses affect \speculake
and how further variants of Spectre can be adapted to \speculake. Current
analysis techniques for reverse engineering are insufficient to reason about the
behavior of these programs.

%Given the benefits that speculative execution provides to an attacker and the
%ease of such an attack, the feasibility of an \speculake exploit is high and is
%not limited to data side-channels or process isolation violations, as was
%originally thought in the wake of Spectre. The speculative primitive developed
%in this work not only provides a guarded form of computation, but also enables
%cryptographic protection against current analysis and debugging techniques.
